### 2016-09-09 Chapters/ContributionsSummary.tex
Finish introduction. I'll have to add some stuff later..:
Almost done

The \pcmsolver library was developed to fulfill these requirements and
offer the community an easy-to-use implementation of the \acrshort{PCM}.
\pcmsolver is written in C++ with Fortran, C and Python components.
Architectural and conceptual organization of the code is provided by the
C++ layer. To ensure the largest possible impact, the code is C++03 ISO standard
compliant, with external dependencies kept to a minimum.
Tuples, container algorithms and functional programming tools are not
part of the standard we chose to comply to.
Parts of the Boost C++ libraries are used to alleviate these
shortcomings.~\autocite{boost}
Linear algebra operations are managed through the Eigen C++ template
library.~\autocite{eigen}
The Python layer provides input reading and parsing facilities,
as implemented by the GetKw library.~\autocite{libgetkw}
Cavity construction and discretization is handled either by the Fortan
or by the C layer, depending on which computational \emph{backend} is
needed.
Evaluation of the Green's functions, needed to set up the representation
of the boundary integral operators, leverages \gls{AD}. We use the Taylor library, a template C++
implementation of \acrshort{AD}.~\autocite{Bartholomew-Biggs2000-db, libtaylor}
The adoption of \git as \acrshort{DVCS}, \cmake for cross-platform builds and
automatic documentation deployment on \readthedocs simplify
extensibility of the module and promote third-party contributions to the
code base. Continuous integration and nightly testing offer an
invaluable level of confidence in the code.

@@

\section{Continuum solvation in the relativistic regime}\label{sec:relapcm}

@@

\section{Non homogeneous environments}\label{sec:spherical}

@@

\section{Open-ended self-consistent field response theory in
solution}\label{sec:pcmopenrsp}

>>>>

The \pcmsolver library was developed to fulfill these requirements and
offer the community an easy-to-use implementation of the
\acrshort{PCM}.\autocite{PCMSolver}
\pcmsolver is written in C++ with Fortran, C and Python components.
Architectural and conceptual organization of the code is provided by the
C++ layer. To ensure the largest possible impact, the code is C++03 ISO standard
compliant, with external dependencies kept to a minimum.
Tuples, container algorithms and functional programming tools are not
part of the standard we chose to comply to.
Parts of the Boost C++ libraries are used to alleviate these
shortcomings.~\autocite{boost}
Linear algebra operations are managed through the Eigen C++ template
library.~\autocite{eigen}
The Python layer provides input reading and parsing facilities,
as implemented by the GetKw library.~\autocite{libgetkw}
Cavity construction and discretization is handled either by the Fortan
or by the C layer, depending on which computational \emph{backend} is
needed.
Evaluation of the Green's functions, needed to set up the representation
of the boundary integral operators, leverages \gls{AD}. We use the Taylor library, a template C++
implementation of \acrshort{AD}.~\autocite{Bartholomew-Biggs2000-db, libtaylor}
The adoption of \git as \acrshort{DVCS}, \cmake for cross-platform builds and
automatic documentation deployment on \readthedocs simplify
extensibility of the module and promote third-party contributions to the
code base. Continuous integration and nightly testing offer an
invaluable level of confidence in the code.

@@

\section{Continuum Solvation in the Relativistic Regime}\label{sec:relapcm}

@@

\section{Non Homogeneous Environments}\label{sec:spherical}

@@

\section{Open-Ended Self-Consistent Field Response Theory in
Solution}\label{sec:pcmopenrsp}

### 2016-09-09 FrontBackmatter/Abstract.tex
Almost done

\vfill

@@

\vfill

>>>>

Synergistic theoretical and experimental approaches to challenging
chemical problems have become more and more widespread, due to the
availability of efficient and accurate \emph{ab initio} quantum chemical
models.
Limitations to such an approach do, however, still exist.
The vast majority of chemical phenomena happens in complex environments,
where the molecule of interest can interact with a large number of other
moieties, solvent molecules or residues in a protein.
These systems represent an ongoing challenge to our modelling
capabilities, especially when high accuracy is required for the
prediction of exotic and novel molecular properties.
How to achieve the insight needed to understand and predict the physics
and chemistry of such complex systems is still an open question.

I will present our efforts in answering this question based on the
development of the polarizable continuum model for solvation.
While the solute is described by a quantum mechanical method, the
surrounding environment is replaced by a structureless continuum
dielectric.
The mutual polarization of the solute-environment system is described by
classical electrostatics.
Despite its inherent simplifications, the model contains the basic
mathematical features of more refined explicit quantum/classical
polarizable models.
Leveraging this fundamental similarity, we show how the
inclusion of environment effects for relativistic and nonrelativistic
quantum mechanical Hamiltonians, arbitrary order response properties and
high-level electron correlation methods can be transparently derived and
implemented.
We implemented an application programming interface that can provide the
continuum solvation functionality to any quantum chemistry software.
As examples of the flexibility of our implementation approach, we
present results for the continuum modelling of non homogeneous environments and
how wavelet-based numerical methods greatly outperform the accuracy of
traditional methods usually employed in continuum solvation models.

@@

\begin{flushright}
    \begin{tabular}{m{5cm}}
      \textit{\myLocation, \myTime} \\
      \includegraphics[width=0.4\textwidth]{gfx/signature.png} \\
        \hline
        \centering\myName \\
    \end{tabular}
\end{flushright}

### 2016-09-09 FrontBackmatter/Notation.tex
Work on MQM chapter
Write another section in the introduction
Adjust TOC bookmarks
Almost done

%\chapter*{Notations, conventions and units}
\addcontentsline{toc}{chapter}{\tocEntry{Notations, conventions and units}}

@@

\renewcommand{\nomname}{
Notations, Conventions and Units
}

\renewcommand{\nompreamble}{
A number of notations and typographic conventions has been adopted in
order to maintain consistency throughout. We summarize them here.
Hartree atomic units are used throughout:~\autocite{Whiffen1978-xx, Mohr2012-zc}
\begin{equation*}
  \si{\electronmass} = \si{\elementarycharge} = \hslash = 4\pi\diel_0 = 1
\end{equation*}
the unit of length is the Bohr \si{\bohr}, while that of energy is the Hartree \si{\hartree}.
The speed of light is then:
\begin{equation*}
  c = \SI{137.035999074}{\bohr\hartree\per\planckbar}
\end{equation*}
}

% Basic Notation
\nomenclature[A, 01]{$u_E$}{Restriction (trace) of the function $u$ to the set $E$}
\nomenclature[A, 02]{$\Span{\vect{v}_1, \ldots, \vect{v}_n}$}{Vector space spanned by the vectors $\vect{v}_1, \ldots, \vect{v}_n$}
\nomenclature[A, 03]{$\delta_{ij}$}{Kronecker symbol: $\delta_{ij}=1i$ if $i=j$ and 0 otherwise}
\nomenclature[A, 04]{$\scalprod[X]{u}{v}$}{Scalar product of $u$ and $v$ in the Hilbert space $X$}
\nomenclature[A, 05]{$\norm{u}{X}$}{Norm of $u$ in the normed space $X$}
% Vectors and Matrices
\nomenclature[B, 01]{$\vect{v}, \vect{q}$}{Vectors}
\nomenclature[B, 02]{$\mat{K}, \mat{F}$}{Matrices}
\nomenclature[B, 03]{$\mathbb{R}^{m, n}$}{Vector space of real-valued $m\times n$ matrices}
\nomenclature[B, 04]{$\Tr\mat{A}$}{Trace of $\mat{A}$. For $\mat{A}\in\mathbb{R}^{n, n}$, $\Tr\mat{A}=\sum_{i=1}^n A_{ii}$}
\nomenclature[B, 05]{$0_N, I_N$}{The zero and the identity in an $N$-dimensional vector space}
% Operators
\nomenclature[C, 01]{$\bi{A}, \bi{D}$}{Integral operators}
\nomenclature[C, 02]{$H, \varPhi$}{First or second quantized $N$-electron operators}
% Function Spaces
\nomenclature[D, 02]{$\mathcal{C}^0(\Omega)$}{Space of continuous functions on $\Omega\subset\mathbb{R}^d$}
\nomenclature[D, 03]{$\mathcal{C}^k(\Omega)$}{Space of $k$ times continuously differentiable functions on $\Omega$}
\nomenclature[D, 04]{$L^p(\Omega)$}{Space of functions whose $p$-th power is Lebesgue integrable on $\Omega$}
\nomenclature[D, 05]{$\norm{u}{0, p, \Omega}$}{Norm in $L^p(\Omega)$: $\norm{u}{0, p, \Omega} = (\int_\Omega\diff\vect{r} |u(\vect{r})|^p)^\frac{1}{p}$}
\nomenclature[D, 06]{$\norm{u}{\Omega}$}{Norm in $L^2(\Omega)$: $\norm{u}{\Omega} = \norm{u}{0, 2,\Omega} = \sqrt{\int_\Omega\diff\vect{r} |u(\vect{r})|^2}$}
\nomenclature[D, 07]{$H^s(\Omega)$}{Sobolev space of order $s$ of functions whose derivative up to order $s$ are in $L^2(\Omega)$}
\nomenclature[D, 08]{$H_0^s(\Omega)$}{Space of functions in $H^2(\Omega)$ with null trace on the boundary of $\Omega$}
\nomenclature[D, 09]{$|u|_{s, \Omega}$}{Seminorm in $H^s(\Omega)$: $|u|_{s, \Omega} \coloneq \sum_{|\alpha|=s}\norm{\partial^\alpha u}{\Omega}$}
\nomenclature[D, 10]{$\norm{u}{s, \Omega}$}{Norm in $H^s(\Omega)$: $\norm{u}{s, \Omega} \coloneq \sum_{l \leq s} |u|_{l, \Omega}$}
% Molecular Quantum Mechanics
\nomenclature[E, 01]{$r, s, t$}{General \acrlong*{MO} indices}
\nomenclature[E, 02]{$i, j, k$}{Occupied \acrlong*{MO} indices}
\nomenclature[E, 03]{$a, b, c$}{Virtual \acrlong*{MO} indices}
\nomenclature[E, 04]{$\kappa, \lambda, \mu$}{One-electron basis functions indices}

>>>>

@@

\renewcommand{\nomname}{Notations, Conventions and Units}

\renewcommand{\nompreamble}{
A number of notations and typographic conventions has been adopted in
order to maintain consistency throughout. We summarize them here.
Hartree atomic units are used throughout:~\autocite{Whiffen1978-xx, Mohr2012-zc}
\begin{equation*}
  \si{\electronmass} = \si{\elementarycharge} = \hslash = 4\pi\diel_0 = 1
\end{equation*}
the unit of length is the Bohr \si{\bohr}, while that of energy is the Hartree \si{\hartree}.
The speed of light is then:
\begin{equation*}
  c = \SI{137.035999074}{\bohr\hartree\per\planckbar}
\end{equation*}
Complex conjugation will always be shown using a dagger ($\dagger$)
instead of a star ($*$).
}

\refstepcounter{dummy}
\phantomsection
\addcontentsline{toc}{chapter}{\tocEntry{\nomname}}

% Basic Notation
\nomenclature[A, 01]{$u_E$}{Restriction (trace) of the function $u$ to the set $E$}
\nomenclature[A, 02]{$\Span{\vect{v}_1, \ldots, \vect{v}_n}$}{Vector space spanned by the vectors $\vect{v}_1, \ldots, \vect{v}_n$}
\nomenclature[A, 03]{$\delta_{ij}$}{Kronecker symbol: $\delta_{ij}=1i$ if $i=j$ and 0 otherwise}
\nomenclature[A, 04]{$\scalprod[X]{u}{v}$}{Scalar product of $u$ and $v$ in the Hilbert space $X$}
\nomenclature[A, 05]{$\norm{u}{X}$}{Norm of $u$ in the normed space $X$}
\nomenclature[A, 06]{$O(N)$}{A quantity of order $N$ or higher}
% Vectors and Matrices
\nomenclature[B, 01]{$\vect{v}, \vect{q}$}{Vectors}
\nomenclature[B, 02]{$\mat{K}, \mat{F}$}{Matrices}
\nomenclature[B, 03]{$\mathbb{R}^{m, n}$}{Vector space of real-valued $m\times n$ matrices}
\nomenclature[B, 04]{$\Tr\mat{A}$}{Trace of $\mat{A}$. For $\mat{A}\in\mathbb{R}^{n, n}$, $\Tr\mat{A}=\sum_{i=1}^n A_{ii}$}
\nomenclature[B, 05]{$\eqtr$}{The expression following is to be interpreted as a trace. $\mathcal{E} \eqtr \mat{h}\mat{D} = \Tr\mat{h}\mat{D}$}
\nomenclature[B, 06]{$\eqavetr$}{The expression following is to be interpreted as a trace followed by time-averaging over a period $T$.
$\mathcal{E} \eqavetr \mat{h}\mat{D} = \frac{1}{T}\int_{0}^{T}\diff t\Tr\mat{h}\mat{D}$}
\nomenclature[B, 07]{$0_N, I_N$}{The zero and the identity in an $N$-dimensional vector space}
% Operators
\nomenclature[C, 01]{$\bi{A}, \bi{D}$}{Integral operators}
\nomenclature[C, 02]{$H, \varPhi$}{First or second quantized $N$-electron operators}
% Function Spaces
\nomenclature[D, 02]{$\mathcal{C}^0(\Omega)$}{Space of continuous functions on $\Omega\subset\mathbb{R}^d$}
\nomenclature[D, 03]{$\mathcal{C}^k(\Omega)$}{Space of $k$ times continuously differentiable functions on $\Omega$}
\nomenclature[D, 04]{$L^p(\Omega)$}{Space of functions whose $p$-th power is Lebesgue integrable on $\Omega$}
\nomenclature[D, 05]{$\norm{u}{0, p, \Omega}$}{Norm in $L^p(\Omega)$: $\norm{u}{0, p, \Omega} = (\int_\Omega\diff\vect{r} |u(\vect{r})|^p)^\frac{1}{p}$}
\nomenclature[D, 06]{$\norm{u}{\Omega}$}{Norm in $L^2(\Omega)$: $\norm{u}{\Omega} = \norm{u}{0, 2,\Omega} = \sqrt{\int_\Omega\diff\vect{r} |u(\vect{r})|^2}$}
\nomenclature[D, 07]{$H^s(\Omega)$}{Sobolev space of order $s$ of functions whose derivative up to order $s$ are in $L^2(\Omega)$}
\nomenclature[D, 08]{$H_0^s(\Omega)$}{Space of functions in $H^2(\Omega)$ with null trace on the boundary of $\Omega$}
\nomenclature[D, 09]{$|u|_{s, \Omega}$}{Seminorm in $H^s(\Omega)$: $|u|_{s, \Omega} = \sum_{|\alpha|=s}\norm{\partial^\alpha u}{\Omega}$}
\nomenclature[D, 10]{$\norm{u}{s, \Omega}$}{Norm in $H^s(\Omega)$: $\norm{u}{s, \Omega} = \sum_{l \leq s} |u|_{l, \Omega}$}
% Molecular Quantum Mechanics
\nomenclature[E, 01]{$r, s, t$}{General \acrlong*{MO} indices}
\nomenclature[E, 02]{$i, j, k$}{Occupied \acrlong*{MO} indices}
\nomenclature[E, 03]{$a, b, c$}{Virtual \acrlong*{MO} indices}
\nomenclature[E, 04]{$\kappa, \lambda, \mu$}{One-electron basis functions indices}
